Compiling refinement types to dependent types

### 2020-07-20 tex/paper.tex
Start writing the terms translation the right way

\paragraph{Terms.}
Finally we define $\tranderiv$.
As it is defined on typing derivation trees,
we consider the term typing rule that is used last to prove $\nonterm G \vdash \nonterm{es} : \nonterm{ts}$.

\begin{itemize}
  \item \ranchor{T-Unit}.
    This rule has no premises, so we just translate it into \ranchor{CT-UnitTerm}:
    \[
      \inferrule{ }{\nonterm G \vdash \unit : \{ \gterm v : \Unit | \top \}} \longmapsto \inferrule{ }{\nonterm{GC} \vdash \unitc : \Unitc}
    \]
\end{itemize}

\begin{equation}
\begin{aligned}
  & \tranterm(x) &&
    \triangleq x                                                              \\
  & \tranterm(\lambda x : \nonterm{ts}. \nonterm{es})  &&
    \triangleq \lambda x : \tranty(\nonterm{ts}). \tranterm(\nonterm{es})     \\
  & \tranterm(\nonterm{es}_1 \nonterm{es}_2)  &&
    \triangleq \tranterm(\nonterm{es}_1) \tranterm(\nonterm{es}_2)            \\
\end{aligned}
\end{equation}

>>>>

\paragraph{Terms.}
Finally we define $\Tranterm$.
We consider the term typing rule that is at the root of the derivation tree for $\nonterm G \vdash \nonterm{es} : \nonterm{ts}$.

\begin{itemize}
  \item \ranchor{T-Unit}.
    \begin{align*}
      & \inferrule{\nonterm G \text{ ok}}{\nonterm G \vdash \unit : \{ \gterm v : \Unit | \top \}}
          \longmapsto
        \inferrule{ }{\nonterm{GC} \vdash \unitc : \Unitc}, \\
      \text{where}~&\nonterm{GC} = \tranctx(\nonterm G \text{ ok}).
    \end{align*}
    This rule has a single premise $\nonterm G \text{ ok}$ that the surface context is well-formed.
    We use $\Tranctx$ to translate the surface derivation of that premise into the core one,
    and extract the resulting context $\nonterm{GC}$.
    We then use that context for \ranchor{CT-UnitTerm}.
\end{itemize}
